Interactive Visualization of Hierarchically Structured Data

### 2016-12-06 treelapse.Rmd
Use pdf figures for antibiotic and pregnancy examples

```{r antibioticoverview, fig.cap = "The two antibiotic time courses are readily apparent even when only highlighting the most abundant taxa."}
knitr::include_graphics("antibiotic_overview.png")
```

```{r antibioticbacteroidetes, fig.cap = "Introducing a second box into the timebox display identifies the Bacteroidaceae as a taxon only midly impacted by antibiotics."}
knitr::include_graphics("antibiotic_bacteroidetes.png")
```

@@

```{r antibioticfirmicutes, fig.cap = "Zooming into the second antibiotic timecourse and highlighting the Lachnospiraceae and Ruminococcus, we see that the Ruminoccocus took more time to recover to pre-treatment levels."}
knitr::include_graphics("antibiotic_firmicutes.png")
```

@@

```{r ruminococcus, fig.cap = "By hovering over the Ruminoccocus branches, we see that there is a prolonged effect of the antibiotics time courses more or less uniformly across the lower taxonomic orders, with the except of "}
knitr::include_graphics("ruminococcus.png")
```

@@

```{r verrucomicrobiae, fig.cap = "The subtree averages aggregation brings attention to the Verrucomicrobiae, which though only present as a few species, are each rather abundant. In particular, they seem to increase after the first antibiotic time course."}
knitr::include_graphics("verrucomicrobiae.png")
```

@@

```{r pretermcsts, fig.cap = "The increased diversity among samples in CST 4 is represented by the relatively larger contribution of red edges to branches outside of the Firmicutes."}
knitr::include_graphics("preterm_csts.png")
```

```{r pretermcstslacto, fig.cap = "Zooming into the Lactobacillaceae family, we notice that the difference between the remaining four CSTs is related to which types of Lactobacillus are most prominent."}
knitr::include_graphics("preterm_csts_lacto.png")
```

>>>>

```{r antibioticoverview, fig.cap = "The two antibiotic time courses are readily apparent even when only highlighting the most abundant taxa."}
knitr::include_graphics("figure/antibiotic_overview.pdf")
```

```{r antibioticbacteroidetes, fig.cap = "Introducing a second box into the timebox display identifies the Bacteroidaceae as a taxon only midly impacted by antibiotics."}
knitr::include_graphics("figure/antibiotic_bacteroidetes.pdf")
```

@@

```{r antibioticfirmicutes, fig.cap = "Zooming into the second antibiotic timecourse and highlighting the Lachnospiraceae and Ruminococcus, we see that the Ruminoccocus took more time to recover to pre-treatment levels."}
knitr::include_graphics("figure/antibiotic_firmicutes.png")
```

@@

```{r ruminococcus, fig.cap = "By hovering over the Ruminoccocus branches, we see that there is a prolonged effect of the antibiotics time courses more or less uniformly across the lower taxonomic orders, with the except of "}
knitr::include_graphics("figure/ruminococcus.pdf")
```

@@

```{r verrucomicrobiae, fig.cap = "The subtree averages aggregation brings attention to the Verrucomicrobiae, which though only present as a few species, are each rather abundant. In particular, they seem to increase after the first antibiotic time course."}
knitr::include_graphics("figure/verrucomicrobiae.pdf")
```

@@

```{r pretermcsts, fig.cap = "The increased diversity among samples in CST 4 is represented by the relatively larger contribution of red edges to branches outside of the Firmicutes."}
knitr::include_graphics("figure/preterm_csts.pdf")
```

```{r pretermcstslacto, fig.cap = "Zooming into the Lactobacillaceae family, we notice that the difference between the remaining four CSTs is related to which types of Lactobacillus are most prominent."}
knitr::include_graphics("figure/preterm_csts_lacto.png")
```
